---
title: "brewsTest"
author: "Kebur Fantahun, Ricco Ferraro" 
date: "02/21/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir= normalizePath('..'))
knitr::opts_chunk$set(error = FALSE)
```

# Introduction 
## Restatment of problem
stuff goes here
## Dataset
stuff goes here
## Techniques used
stuff goes here

# Libraries 
```{r load-packages}
library(tidyverse)
library(magrittr)
library(knitr)
library(rmarkdown)
library(DT)
library(mice)
library(VIM)
library(psych)
library(tidyverse)
library (readr)
library(caret)
```


# Utility functions 
```{r}

isEmpty <- function(column) {
    is.na(column) | column == 0 | column == "" | column == " " | column == "NA" | column == "na" | column == "Na" | column == "nA" | column == "NaN" 
}
```


# Import Data 
```{r message=FALSE, warning=FALSE}

# Todo update this to just use file in current directory (which should exist because it is commited to the same repository in source control)
beer_url="https://raw.githubusercontent.com/RiccoFerraro/dds_case_study_1/main/Beers.csv?token=ADHK27V7NC2MST3MBWULDE3AJLWSC"
brewery_url="https://raw.githubusercontent.com/RiccoFerraro/dds_case_study_1/main/Breweries.csv?token=ADHK27SX6GX255OHB7MNDVDAJLWVQ"

beer <-read_csv(url(beer_url))
brew <-read_csv(url(brewery_url))
```
*Note: we use the merge data in Question 1 and therefor we need to perform step 2 first.*
# 2. Merge beer data first with the breweries data & Print first 6 and last 6 oservations in merged file. 
```{r}
## EDA: Formatting, and dealing with NA's

# beer$Brewery_id
# names(beer)[names(beer) == "Brewery_id"] <- "Brew_ID"

bdat = merge(beer, brew, by.x = "Brewery_id", by.y = "Brew_ID")
names(bdat)[names(bdat) == "Name.x"] <- "Drink_name"
names(bdat)[names(bdat) == "Name.y"] <- "Brewery"

kable(head(bdat))
kable(tail(bdat))

```


# 1. How many breweries are in each state?
See Table:
```{r}
bdat$State = as.factor(bdat$State)
brewNum = bdat %>% 
  filter(!is.na(bdat) & !is.na(Brewery_id)) %>% 
  group_by(State) %>% summarize(unique_breweries=length(unique(Brewery_id))) 

datatable(brewNum)

print("Total Unique Breweries: ")
sum(brewNum$unique_breweries)

brewNum %>%  ggplot(aes(x=unique_breweries, y="",fill=State)) + geom_bar(stat = "identity", colour="black") + coord_polar("x", start=0) + ggtitle("Unique Breweries By state")
```

# 3a. Plot missing data for reference
```{r}
# Plot missing data (there should be none)
bdat_mice_clean <- aggr(bdat, col=c('navyblue','yellow'),
                    numbers=TRUE, sortVars=TRUE,
                    labels=names(bdat), cex.axis=.7,
                    gap=3, ylab=c("Missing data","Pattern"))
summary(bdat)
```



# 3b. Assess missing data when no data exists for IBU OR ABV
1. Special Release, The Crowler^tm, Can'd aid foundation are missing ABV/IBU/Style
2. Cedar creek - Special Release is ambiguous, missing ABV/IBU/Style and will be dropped as it does not solve the QOI. 
3. Oskar Blues Brewery - The Crowler is not an actual beer but a type of can
4. Oskar Blues Brewery - Can'd aid foundation is a relief effort that sends water so it does not fit in the dataset.
5. Beer ID 2364, Royal Lager of Weston Brewing has no ABV/IBU
6. Same for BID - 2322	Fort Pitt Brewing Company	Fort Pitt Ale
7. Oskar Blues Brewery	Birth IPA, 1750
8. 710, no data
9. MillKing It Productions	AXL Pale Ale, 273 - out of business no info
10. 1095 no data
11. 963 no data
```{r}
# the following line removes these NA points
bdat_clean <- bdat %>% filter(bdat$Beer_ID!=2210 & bdat$Beer_ID!=1796 & bdat$Beer_ID!=1790 & bdat$Beer_ID!=2364&
bdat$Beer_ID!=2322& bdat$Beer_ID!=1750& bdat$Beer_ID!=710& bdat$Beer_ID!=273& bdat$Beer_ID!=1095& bdat$Beer_ID!=963)

```



# 3c. Enter in missing data when by hand when data is availbe publicly 
-Add style data for 2527 and 1635 by looking it up by hand. 
-Add IBU and ABV Data for many missing rows by looking up by hand (online via `BeerAdvocate.com` or `Untappd.com`)
```{r}
imputeMissingStyle <- function(beer_id, style){
    if(beer_id=="2527"){
    style = "Scottish-Style Amber Ale"
  } 
    if(beer_id=="1635"){
    style = "Lager"
    } 
  style
}

# Update ABV and IBU for NA's; to hand selected data use  %>% select(Beer_ID, Brewery, Drink_name, ABV, IBU)
bdat_hand_updated <-bdat_clean %>% 
    filter(is.na(ABV) & is.na(IBU)) %>% rows_update(tibble(Beer_ID = c(2382, 2381, 1948, 1347, 2595, 1163, 940, 2490, 2489, 2488, 2487, 2472, 779, 364, 60, 59, 58, 57, 652, 2344, 2342, 1752, 61, 1724, 774, 121, 1784, 1541, 1025, 219, 307, 1096, 1056, 944, 731, 870, 869, 868, 867, 763, 504, 524, 450, 449, 448, 447, 446, 520, 506, 142, 335, 64), ABV = c(0.075, 0.055, 0.045, 0.060, 0.062, 0.0499, 0.06, 0.061, 0.038, 0.057, 0.051, 0.055, 0.05, 0.07, 0.052, 0.05, 0.049, 0.051, 0.07, 0.055, 0.049, 0.07, 0.052, 0.07, 0.058, 0.052, 0.07, 0.052, 0.086, 0.051, 0.06, 0.062, 0.055, 0.05, 0.055, 0.042, 0.05, 0.045, 0.039, 0.052, 0.072, 0.045, 0.061, 0.064, 0.058, 0.049, 0.05, 0.042, 0.05, 0.065, 0.065, 0.05), IBU = c(NA, 3.57, 65, 23, NA, 15, NA, 40, 7, 32, 35, NA, 5, NA, NA, NA, NA, NA, 80, NA, NA, NA, 28, NA, NA, 12, 40, 21, 80, NA, 38, NA, NA, 25, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, 70, 17)))

bdat_with_hand_updates = merge(bdat_hand_updated,bdat_clean,by="Beer_ID",all.y = TRUE) %>% rowwise %>% mutate(Brewery_id=Brewery_id.y, Drink_name=Drink_name.y, Ounces
=Ounces.y, Brewery=Brewery.y, City=City.y, State=State.y, Style = imputeMissingStyle(Beer_ID, Style.y),IBU = if_else(isEmpty(IBU.y), IBU.x, IBU.y), ABV = if_else(isEmpty(ABV.y), ABV.x, ABV.y)) %>% select(Brewery_id, ABV, IBU, Drink_name, Style, Ounces, Brewery, City, State)
```



# 3d. Assess and impute missing IBU data with median IBU by style 
```{r}
#Summary stats before imputation
kable(summary(bdat_with_hand_updates))

# Impute IBU
bdat.IBU.Summary <- bdat_with_hand_updates %>% filter(!isEmpty(IBU)) %>% group_by(Style) %>% summarise(median_IBU_by_style=median(IBU))
bdat.imputed.IBU <-merge(bdat_with_hand_updates, bdat.IBU.Summary, by="Style")  %>% mutate(IBU.clean = if_else(isEmpty(IBU), median_IBU_by_style, as.double(IBU)))
bdat.imputed.IBU.clean = bdat.imputed.IBU[,-c(4)]
bdat.imputed.IBU.clean %>% filter(isEmpty(Style))

# Summary stats after imputation
kable(summary(bdat.imputed.IBU.clean))
```



# 3e. Plot missing data to show it has all been resolved. 
```{r}
# Plot missing data (there should be none)
bdat_mice_clean <- aggr(bdat.imputed.IBU.clean, col=c('navyblue','yellow'),
                    numbers=TRUE, sortVars=TRUE,
                    labels=names(bdat.imputed.IBU.clean), cex.axis=.7,
                    gap=3, ylab=c("Missing data","Pattern"))
summary(bdat.imputed.IBU.clean)
```



# 4. Median ABV and IBU per state (See output for values)
```{r}
median.imputed.by.state <- bdat.imputed.IBU.clean  %>% 
  group_by(State) %>% summarize(median_abv=median(ABV), median_ibu=median(IBU.clean)) 

median.imputed.by.state %>% ggplot(aes(y=median_abv, x=State, fill=State)) + geom_bar(stat="identity")+ ggtitle("Median ABV by state")

median.imputed.by.state %>% ggplot(aes(y=median_ibu, x=State, fill=State)) + geom_bar(stat="identity") + ggtitle("Median IBU by state")
print("Total Unique Breweries: ")
sum(brewNum$unique_breweries)
```




# 5.  Which state has the maximum alcoholic (ABV) beer? Which state has the most bitter (IBU) beer? (See output for values)
```{r}
kable(head(arrange(bdat.imputed.IBU.clean, desc(ABV))))
print("highest ABV State")
arrange(bdat.imputed.IBU.clean, desc(ABV))[1,]

kable(head(arrange(bdat.imputed.IBU.clean, desc(IBU.clean))))
print("highest IBU State")
arrange(bdat.imputed.IBU.clean, desc(IBU.clean))[1,]
```





# 6. Summary statistics and Histogram for ABV
```{r}
kable(summary(bdat.imputed.IBU.clean))

bdat.imputed.IBU.clean %>% ggplot(aes(x=ABV, fill=State)) + geom_histogram(binwidth = .003)
bdat.imputed.IBU.clean %>% ggplot(aes(x=IBU.clean, fill=State)) + geom_histogram()
```

# 7a. Summary statistics and Histogram for ABV
```{r}
bdat.imputed.IBU.clean %>% ggplot(aes(x=ABV, y=IBU.clean, colour=State)) + geom_point() + ggtitle("IBU vs ABV")
bdat.imputed.IBU.clean %>% ggplot(aes(x=ABV, y=IBU.clean)) + geom_smooth() + ggtitle("IBU vs ABV")
```

# 7b. EDA continued
TODO: Speak to Assumptions for Linear Regression, and P-value and confidence interval for ABV estimate, scope of inference
```{r}
#Linear-Linear
linearlinear <- lm(IBU.clean~State + State*ABV + ABV, data=bdat.imputed.IBU.clean)
plot(linearlinear)
summary(linearlinear)
```


# 8. Difference with respect to IBU and ABV between IPAs and other Ales
To investigate the difference between `IBU` and `ABV` for `IPA's vs OtherAles` we first perform some nominal data cleanup and visualize IBU vs ABV for `IPA's vs otherAles`. We then use KNN to classify style, either `IPA` or `otherAle`, to highlight that there is a significant difference between the relationship of IBU and ABV for `IPA's` and `otherAles`

## Data Prep and Visualization 
1. Filter out all data that is not an `Ale`. Then bucket anything with `IPA` or `India Pale Ale` as `IPA` and all other beers with the word `Ale` in their style as `OtherAle`.  
2. Then plot IBU and ABV for `IPA's` and `otherAles` for IPA's and OtherALes
**Note: American Pale Ale is VERY similar to IPA but we call it "other" ale**
```{r}
summary(as.factor(bdat.imputed.IBU.clean$Style))
bdat.IPA.Vs.Ales = bdat.imputed.IBU.clean %>% mutate(Style = if_else(str_detect(Style, "India Pale Ale|IPA"), "IPA", if_else(str_detect(Style, "Ale"),"OtherAle", Style))) %>% filter(Style == "IPA" | Style == "OtherAle") %>% mutate(Style = as.factor(Style))
head(bdat.IPA.Vs.Ales)
bdat.IPA.Vs.Ales %>% ggplot(aes(x=ABV, y=IBU.clean, colour= Style)) + geom_point()

summary(bdat.imputed.IBU.clean$Style)
```
## Test split
Split the data into 85% train and 15% test. Only train our algorithms on training data with crossvalidation. Use test split only for accuracy and prediction metric calculation. 
```{r}
set.seed(1234)
splitPercKNN = .85
trainIndicesKNN = sample(1:dim(bdat.IPA.Vs.Ales)[1],round(splitPercKNN * dim(bdat.IPA.Vs.Ales)[1]))
bdat.IPA.Vs.Ales.train = bdat.IPA.Vs.Ales[trainIndicesKNN,]
bdat.IPA.Vs.Ales.test = bdat.IPA.Vs.Ales[-trainIndicesKNN,]
```

## KNN for `IPA's` vs `Other Ales`
```{r}
trControl <- trainControl(method  = "cv",
                          number  = 10)

fit.bothScaled <- train(Style ~ IBU.clean + ABV,
             method     = "knn",
             preProcess = c("center", "scale"),
             tuneGrid   = expand.grid(k = 1:10),
             trControl  = trControl,
             metric     = "Accuracy",
             data       = bdat.IPA.Vs.Ales.train)

# fit.Both appears to perform the best as far as accuracy goes. 

classifications <- predict(fit.bothScaled, bdat.IPA.Vs.Ales.test)
CM = confusionMatrix(table(bdat.IPA.Vs.Ales.test$Style, classifications))
CM
```

## OLS Multiple Linear Regression for `IPA's` vs `Other Ales`
Use least squared multiple linear regression to highlight specific relationships between IBU and ABV for style IPA and style otherAle. 
- NOTE: make the unit increase in interpretation be in terms of .01 unit increase in ABV
```{r}
linearlinear <- lm(IBU.clean~Style +Style*ABV + ABV, data=bdat.IPA.Vs.Ales.train)
plot(linearlinear)
confint(linearlinear)
summary(linearlinear)
```

## LDA and KNN to predict style based on IBU and ABV Individually
Here we use LDA and KNN to assess the relationship between IBU and Style as well as ABV and style. 
```{r}
lda.fit.IBU = train(Style ~ IBU.clean, data=bdat.IPA.Vs.Ales.train, method="lda",
                trControl = trainControl(method = "cv"),
                             metric     = "Accuracy")

knn.fit.IBU <- train(Style ~ IBU.clean,
             method     = "knn",
             tuneGrid   = expand.grid(k = 1:10),
             trControl  = trControl,
             metric     = "Accuracy",
             data       = bdat.IPA.Vs.Ales.train)

lda.fit.ABV = train(Style ~ ABV, data=bdat.IPA.Vs.Ales.train, method="lda",
                trControl = trainControl(method = "cv"),
                             metric     = "Accuracy")

knn.fit.ABV <- train(Style ~ ABV,
             method     = "knn",
             tuneGrid   = expand.grid(k = 1:10),
             trControl  = trControl,
             metric     = "Accuracy",
             data       = bdat.IPA.Vs.Ales.train)

```

## Conclusion: 


# 9.  We will knock your socks off! 
To show that there is a relationship between State and Ounces for all Ales, specifically  12 vs 16 ounces, we perform a brief analysis of Ounces vs. State. What we are interested in here is whether or not a State like California or Michigan  differ in their preference for 12 vs 16 ounce beers. 

## Data Cleanup and Visualization 
1. Filter out all ales that are not either `12` or `16` ounces in volume. 
2. We plot the ratios of `12` vs `16` ounce Ales for each state.  
```{r}
bdat.IPA.Vs.Ales.train.Extra = data.frame(bdat.IPA.Vs.Ales.train, stringsAsFactors=TRUE)
bdat.IPA.Vs.Ales.test.Extra = data.frame(bdat.IPA.Vs.Ales.test, stringsAsFactors=TRUE)
bdat.IPA.Vs.Ales.train.Extra$Ounces = as.factor(bdat.IPA.Vs.Ales.train.Extra$Ounces)
bdat.IPA.Vs.Ales.test.Extra$Ounces = as.factor(bdat.IPA.Vs.Ales.test.Extra$Ounces)
bdat.IPA.Vs.Ales.train.Extra.filtered <- bdat.IPA.Vs.Ales.train.Extra  %>% filter(Ounces=="12" | Ounces=="16") %>% mutate(Ounces=as.factor(as.double(as.character(Ounces))))
bdat.IPA.Vs.Ales.test.Extra.filtered <-  bdat.IPA.Vs.Ales.test.Extra  %>% filter(Ounces=="12" | Ounces=="16") %>% mutate(Ounces=as.factor(as.double(as.character(Ounces))))

#bdat.IPA.Vs.Ales.train.Extra.filtered %>% ggplot(aes(y = IBU.clean, x=as.double(as.character(bdat.IPA.Vs.Ales.train.Extra$Ounces)))) +  geom_smooth(method=lm)
bdat.IPA.Vs.Ales.train.Extra.filtered %>% ggplot(aes(x=Ounces, fill=State)) + geom_bar() + facet_wrap(~State) + ggtitle("Count of 12 and 16 Ounce ales by State")
```

## Analysis: KNN & confusion matrix
1. We use KNN with the optimal cross validated value of K (usually k=8) to predict Ounces (12 or 16) by state. 
2. Generate a confusion matrix via test data to assess the performance of the prediction
3. Accuracy ends up being around 0.7137 which is roughly 21% better than the existing random chance that we would have for predicting either 12 or 16 ounces. 
```{r}
set.seed(1234)
knn.fit.OuncesByState <- train(Ounces ~ State,
             method     = "knn",
             preProcess = c("center", "scale"),
             tuneGrid   = expand.grid(k = 1:10),
             trControl  = trControl,
             metric     = "Accuracy",
             data       = bdat.IPA.Vs.Ales.train.Extra.filtered)

knn.fit.OuncesByABV

classifications <- predict(knn.fit.OuncesByState, bdat.IPA.Vs.Ales.test.Extra.filtered)
CM = confusionMatrix(table(bdat.IPA.Vs.Ales.test.Extra.filtered$Ounces, classifications))
CM
```

## Conclusion: 
There is a significant relationship between `Ounces` and `State` for Ales that are either 12 vs 16 ounces. We were able to predict ounces by state (for ales) with an accuracy of 71.4% which is significantly better than random chance (50% accuracy). This suggests that when considering what size a beer should be sold in, it could be important to consider what state that beer is going to be brewed in. This helps align sales with the laws and preferences of that state. For example, Indiana has a high prevalence of 16 ounce ales, whereas Colorado or Texas both lean towards 12 ounce ales. It would be preferable to brew and sell 16 ounce beers in states like Indiana (or other states that have more 16 ounce ales) and 12 ounce beers in Colorado (or other states that have more 12 ounce ales). The reason for this association may be due to a variety of reasons including income, weather, local diet, and social norms for beer drinkers.
